---
title: "Covid-19 Data Analysis-Ontario"
date: "`r Sys.Date()`"
output:
  rmdformats::html_clean:
    highlight: kate
---


```{r setup, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## This workbook highlights covid-19 analysis in ontario which includes data from JAN 2020 to MAY 2020.The analysis was done in the peak of pandemic in ontario,Canada

# INSTALL AND LOAD PACKAGES ################################


```{r intall packages}
if (!require("pacman")) install.packages("pacman")

# pacman must already be installed; then load contributed
# packages (including pacman) with pacman
pacman::p_load(pacman, rio, tidyverse,DataExlplorer,Esquisse)
# pacman: for loading/unloading packages
# rio: for importing data
```

# GET THE DATA################################


```{r import data}
df_ont <- import("https://raw.githubusercontent.com/ankitnagarsheth/RNotebooks/master/analysis/covid-19/covidtesting_ont.csv")


glimpse(df_ont)
```
# WRANGLE THE DATA ################################


```{r wrange the data}
df_ont <- df_ont %>%  mutate(`Reported Date` = as.factor(`Reported Date`)) 

colnames(df_ont)[1] <- "Date"
glimpse(df_ont)

df_ont <- df_ont %>% separate(Date,c("year","month","day"),sep = "-",remove = FALSE) %>% glimpse()

df_ont <- df_ont %>% mutate(Deathratio = (Deaths/`Total Cases`) * 100) 

glimpse(df_ont)
```
# VISUALIZE ################################

## Total Cases by Month

```{r Total Cases by Month}
df_ont %>%
  filter(!(month %in% "06")) %>%
  ggplot() +
  aes(x = month, y = `Total Cases`) +
  geom_boxplot(fill = "#0c4c8a") +
  theme_minimal()
```

## Total Cases Vs Confirmed Positive (Breakdown by Resolved)

```{r }
df_ont %>%
  filter(!(month %in% "06")) %>%
  ggplot() +
  aes(x = `Total Cases`, y = `Confirmed Positive`, colour = Resolved) +
  geom_line(size = 1.18) +
  scale_color_distiller(palette = "Spectral") +
  labs(x = "Total Cases", y = "Confirmed Positive", title = "Total Cases Vs Confirmed Positive") +
  theme_minimal()

```
## Total Cases Vs Confirmed Positive 

```{r }
df_ont %>%
  filter(!(month %in% "06")) %>%
  ggplot() +
  aes(x = `Total Cases`, y = `Confirmed Positive`, colour = month) +
  geom_line(size = 1.18) +
  scale_color_brewer(palette = "Spectral") +
  labs(x = "Total Cases", y = "Confirmed Positive", title = "Total Cases Vs Confirmed Positive") +
  theme_minimal()

```
## Total Cases Vs Number of Patients in ICU with COVID-19

```{r }

df_ont %>%
  filter(!(month %in% "06")) %>%
  ggplot() +
  aes(x = `Total Cases`, y = `Number of patients in ICU with COVID-19`, colour = month) +
  geom_line(size = 1.18) +
  scale_color_brewer(palette = "Spectral") +
  labs(x = "Total Cases", y = "Number of Patients in ICU with COVID-19 ", title = "Total Cases Vs Number of Patients in ICU with COVID-19 (Breakdown by Month)") +
  theme_minimal()


```

## Death Ratio By Month


```{r }
df_ont %>%
  filter(!(month %in% "06")) %>%
  ggplot() +
  aes(x = month, weight = Deathratio) +
  geom_bar(fill = "#0c4c8a") +
  labs(x = "Month", y = "Death Ratio", title = "Month Vs Death Ratio") +
  theme_minimal()
```

