---
title: "CMHC Housing COVID-19- 2018 TO 2020"
author: "Ankit Nagarsheth"
date: "8/18/2020"
output: html_document
tidy: styler
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	out.width = '100%'
)
```

### The Workbook summarizes the Canadian Housing,starts,completes and constructions during Covid-19. It analysys data from 2018 to 2020.This data was downloaded from https://www150.statcan.gc.ca/ ###

## INSTALL AND LOAD PACKAGES ################################

```{r install packages}
# Install pacman ("package manager") if needed
if (!require("pacman")) install.packages("pacman")

# pacman must already be installed; then load contributed
# packages (including pacman) with pacman
pacman::p_load(pacman,reticulate,rio, tidyverse,rvest,esquisse,ggthemes,ggraph,tidytext,patchwork,wordcloud2,janitor,glue,scales,RSiteCatalyst,skimr,here,rmdformats)



```



```{r import data}


## IMPORT DATA ######
cmhc <- import("https://raw.githubusercontent.com/ankitnagarsheth/RNotebooks/master/analysis/3410015101-noSymbol-2018-2020.csv")

```

```{r gather the data}


df <-  cmhc %>% 
  gather(key = yr,value = measure,-`Housing estimates`, -`Type of unit`)

glimpse(df)
```



## Lets Wrangle the data ####
```{r wrangle the data}


df_cmhc <- df %>% as_tibble()
glimpse(df_cmhc)



df_cmhc %>% count(`Type of unit`,sort = TRUE)

df_cmhc <- df_cmhc %>% 
  mutate(counts = parse_number(measure)) %>% 
  mutate(Housing_Category = as_factor(`Housing estimates`)) %>% 
  mutate(type_of_unit = as_factor(`Type of unit`)) %>% 
  select(Housing_Category,type_of_unit,counts,yr) %>% 
  separate(yr,c("month","year"),sep = "-",remove=FALSE) %>% 
  glimpse()


df_cmhc <- df_cmhc %>% 
  filter(type_of_unit %in%  c("Single-detached units","Semi-detached units","Row units","Apartment and other units"))

df_cmhc <- df_cmhc %>% 
  mutate(yr = parse_date(yr, '%b-%y'))


# Group by


df_cmhc_cat <- df_cmhc %>% 
  group_by(yr,Housing_Category,type_of_unit) %>%
  
  summarise(n = n(),avg = mean(counts),total = sum(counts)) %>% 
  arrange(desc(avg))

```

## VISUALIZE ####

## Insight =  Apartment units have huge volumes  ######

```{r bar chart}




df_cmhc_cat %>%
  filter(!(Housing_Category %in% "Housing under construction")) %>%
  ggplot() +
  aes(x = yr, fill = type_of_unit, weight = total) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal()


```

## Insight =  Housing starts are in huge number and completes are in phases ########



```{r density plot}

df_cmhc_cat %>%
  filter(!(Housing_Category %in% "Housing under construction")) %>%
  ggplot() +
  aes(x = avg, fill = Housing_Category) +
  geom_density(adjust = 1.4) +
  scale_fill_hue() +
  theme_minimal()


```

## Insight = Highest type of units which are started are Apartment units followed by single detached units and then row units ######


```{r bar chart2}

ggplot(df_cmhc_cat) +
  aes(x = Housing_Category, fill = type_of_unit, weight = avg) +
  geom_bar() +
  scale_fill_hue() +
  theme_minimal()
```

##  Insight = Apartment and other units have huge volume in terms of starts,construction and completions ########

```{r histogram}

ggplot(df_cmhc) +
 aes(x = counts, fill = type_of_unit) +
 geom_histogram(bins = 30L) +
 scale_fill_hue() +
 theme_minimal()




